Paper figures

### 2021-02-03 notebooks/paper_plots_1213_pcc_only.Rmd
changed labels and added margin

```{r}
real_random_labels = c('Real\nnetwork','Rewired\nnetwork')
names(real_random_labels)  = c('real','random')
pcc_deg_eff = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=eff_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Effectiveness")+
    xlab("Degree")+
    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
pcc_deg_sens = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=sens_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Sensitivity")+
    xlab("Degree")+
    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
                    labels = c('D','E'),
                   ncol=2)
ggsave('reports/figures/paper_figures_0202_pcc_only/fig2.png',plot=deg_scatter_plots, width=10,height=10)
```

@@

p3 = 
    ggplot()+
#    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Effectiveness degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"))+
    scale_y_continuous(expand = c(0, 0)) 
p4 = 
    ggplot()+
#    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Sensitivity degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
    scale_color_discrete(labels=c('Rewired networks', 'Real network'))+
    scale_y_continuous(expand = c(0, 0)) 
lgn34  <- cowplot::get_legend(p4)
distr_plots <- plot_grid(
          ggdraw(p3+theme(legend.position=''))+
        cowplot::draw_plot(dens_lgn, .45,.45,.5,.5),
ggdraw( p4+theme(legend.position=''))+
        cowplot::draw_plot(dens_lgn, .45,.45,.5,.5),labels=c('F','G'),nrow=1 )
#distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
# nrow=2,rel_heights = c(0.9,0.1))
#ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
plot_grid(dens_plots, deg_scatter_plots, distr_plots, nrow=3,rel_heights = c(0.4,0.3,.3))
ggsave('reports/figures/paper_figures_0202_pcc_only/fig3.png',width=10,height=12)
```

>>>>

```{r}
real_random_labels = c('Genetic\nnetwork','Random\nnetwork')
names(real_random_labels)  = c('real','random')
pcc_deg_eff = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=eff_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Effectiveness")+
    xlab("Degree")+
    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
pcc_deg_sens = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=sens_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Sensitivity")+
    xlab("Degree")+
    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
    theme(strip.text.y = element_text(angle = 0))+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
                    labels = c('D','E'),
                   ncol=2)
ggsave('reports/figures/paper_figures_0202_pcc_only/fig2.png',plot=deg_scatter_plots, width=10,height=10)
```

@@

p3 = 
    ggplot()+
#    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Effectiveness degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"))+
    scale_y_continuous(expand = c(0, 0)) 
p4 = 
    ggplot()+
#    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Sensitivity degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
    scale_color_discrete(labels=c('Random networks', 'Genetic network'))+
    scale_y_continuous(expand = c(0, 0)) 
lgn34  <- cowplot::get_legend(p4)
distr_plots <- plot_grid(
          ggdraw(p3+theme(legend.position=''))+
        cowplot::draw_plot(dens_lgn, .45,.45,.5,.5),
ggdraw( p4+theme(legend.position=''))+
        cowplot::draw_plot(dens_lgn, .45,.45,.5,.5),labels=c('F','G'),nrow=1 )
#distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
# nrow=2,rel_heights = c(0.9,0.1))
#ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
plot_grid(dens_plots, deg_scatter_plots, distr_plots, nrow=3,rel_heights = c(0.4,0.3,.3))
ggsave('reports/figures/paper_figures_0202_pcc_only/fig3.png',width=10,height=12)
```
